Using reference models in feature selection problems \vspace{.1in}

### 2019-09-22 paper/ref_approach.tex
added minimal subset analysis using parallelized data

Addressing the problem of selecting the minimal subset of relevant/predictive features, 
we compare with a simulation study the selection via projection predictive approach, 
via stepwise forward selection with/without a reference model on top and a Bayesian 
stepwise forward selection.
\begin{itemize}
\item projpred (ref model based): reference model is a linear regression over the first 
five supervised principal components, search heuristics is forward search and the predictive 
performance is estimated via 10-fold cross-validation.
\item stepwise selection (data based): it's based on AIC comparison
\item stepwise selection (ref model based): reference model is a linear regression 
over the first five SPC. The reference model point predictions (posterior predictive means $\hat{y}$) 
are used instead of the target variable values $y$. Based on AIC comparison
\item Bayesian stepwise selection (data based): At each step the model fitted is a 
linear regression using RHS prior and the feature excluded is the one with higher 
Bayesian p-value, defined as:
\begin{equation}
\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
\end{equation}
The selection continues if the reduced model has an elpd score higher than the
current fitted model.
\end{itemize}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
  \label{fig:rmse_vs_fdr}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/entropy.pdf}
  \caption{Entropy score for the minimal subset of feature selection.\\}
  \label{fig:entropy}
\end{figure}

>>>>

Addressing the problem of selecting the minimal subset of relevant/predictive features, 
we compare with a simulation study the selection via projection predictive approach, 
via stepwise forward selection with/without a reference model on top and a Bayesian 
stepwise forward selection.
\begin{itemize}
\item projpred (ref model based): reference model is a linear regression over the first 
five supervised principal components, search heuristics is forward search and the predictive 
performance is estimated via 10-fold cross-validation.
\item stepwise selection (data based): it's based on AIC comparison
\item stepwise selection (ref model based): reference model is a linear regression 
over the first five SPC. The reference model point predictions (posterior predictive means $\hat{y}$) 
are used instead of the target variable values $y$. Based on AIC comparison
\item Bayesian stepwise selection (data based): At each step the model fitted is a 
linear regression using RHS prior and the feature excluded is the one with higher 
Bayesian p-value, defined as:
\begin{equation}
\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
\end{equation}
The selection continues if the reduced model has an elpd score higher than the
current fitted model.
\item Bayesian stepwise selection (ref model based): same as the data based, but instead of using the observed data values to fit the models at each step, it uses the observed covariate and the target values predicted by a reference model 
\end{itemize}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
  \label{fig:rmse_vs_fdr}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
  \caption{Entropy score for the minimal subset of feature selection.\\}
  \label{fig:entropy}
\end{figure}
